\texttt{aeons}: approximating the end of nested sampling

### 2024-02-22 paper/paper.tex
new branch for reviewer changes

\section*{Code availability}
A package is in development to implement the endpoint prediction mechanism, for easy plug-in to existing implementations of nested sampling. The latest updates can be found at \href{https://github.com/zixiao-h/aeons}{github.com/zixiao-h/aeons}.

>>>>

\section*{Data availability}
A package is in development to implement the endpoint prediction mechanism, for easy plug-in to existing implementations of nested sampling. The latest updates can be found at \href{https://github.com/zixiao-h/aeons}{github.com/zixiao-h/aeons}.
